On the discovery of K-enhanced and Mg-depleted stars throughout the Milky Way\footnote{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.}

### 2018-05-24 article/msculled.tex
add tables
tables
moved some tables, changed some text, fixed some figures

\subsection{Follow-up observations with Magellan/MIKE}
We acquired high-resolution spectra of three of our candidates as ancillary targets to an existing observing campaign. The three targets (J075043.12+204658.0, J120032.60+024438.2 and J091825.49+172114.5) were selected based on their observability from Las Campanas Observatory, and we used the Magellan Inamori Kyocera Echelle (MIKE) spectrograph on the Magellan Clay telescope \citep{shectman2003magellan,bernstein2003mike}. Exposure times were calculated to achieve a S/N of 30 per pixel at 450\,nm, sufficient to verify the K-enriched and Mg-poor nature of these stars. We reduced the data using the \texttt{CarPy} package \citep{kelson2003}. We used smoothing spline functions to continuum-normalize individual echelle orders, before combining them to produce a continuum-normalized spectrum that is contiguous from 350\,nm to 950\,nm. With the stellar parameters from \lamost, we calculated [K/Fe] and [Mg/Fe] abundances from individual atomic lines by measuring equivalent widths with Gaussian absorption profiles \citep{castelli2004,sneden,casey2014}. From the Magellan/MIKE spectra we confirmed that the K lines in these candidates were unaffected by telluric contamination. The estimated abundances from Magellan/MIKE spectra are consistent (within the uncertainties) of our initial abundance determinations from \lamost\ (Figure \ref{KvsMg}), and are presented in Table \ref{data:magellan}.

@@

\subsection{Detailed chemical abundances}
\label{sec:abundances}

@@

\begin{figure*}
\begin{subfigure}{0.5\textwidth}
	\includegraphics[width=\columnwidth]{NavsFeh.png}
    \caption{[Na/Fe] vs [Fe/H] for the candidate stars.}
    \label{NavsFeh}
\end{subfigure}

\begin{subfigure}{0.5\textwidth}
	\includegraphics[width=\columnwidth]{Navsb.png}
    \caption{[Na/Fe] vs galactic latitude for the candidate stars.}
    \label{Navsb}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
	\includegraphics[width=\columnwidth]{Navsradvel.png}
    \caption{[Na/Fe] vs radial velocity for the candidate stars.}
    \label{Navsradvel}
\end{subfigure}
%\end{figure*}
%\begin{figure*}
%\ContinuedFloat

\caption{A strong bimodality in [Na/Fe] abundances of the candidate stars is observed, with a significant population displaying anomolously high abundances. Due to the apparent near-exclusivity of this population within the disk of the galaxy, and their notably higher E(B-V) values \citep{schlafly2011}, this phenomena is almost certainly due to interstellar dust.}
\end{figure*}

@@

The [K/Fe] abundance ratios in our sample also show an anti-correlation with total metallicity, illustrated in Figure \ref{KvsFe}, which is not present in the bulk of Milky Way stars. It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation. However, we recommend additional high-resolution observations are needed to verify this trend.

@@

\begin{table*}
\centering
\caption{Tabulated data for 10 of the 112 candidate stars. Data for the full sample is available online.}
\label{data}
\begin{tabular}{cccccccccccccc}
\hline
\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{V$_\textrm{r}$} & \textbf{T$_\textrm{eff}$} & $\boldsymbol \log{ \, \textbf{g}}$ & \textbf{{[}Fe/H{]}} & \textbf{{[}$\alpha$/Fe{]}} & \textbf{$\boldsymbol \chi_r ^\textbf{2}$} & \textbf{{[}K/Fe{]}} & \textbf{Error} & \textbf{{[}Na/Fe{]}} & \textbf{Error} \\ 
- & {[}deg{]} & {[}deg{]} & [pixel$^{-1}]$ & {[${\rm km\,s}^{-1}$]} & {[}K{]} & $[{\rm cm\,s}^{-2}]$ & {[}dex{]} & {[}dex{]} & - & {[}dex{]} & {[}dex{]} & {[}dex{]} & {[}dex{]} \\ \hline
J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.26 & 0.86 & 0.23 \\
J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.22 & 0.39 & 0.22 \\
J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.21 & -0.20 & 0.20 \\
J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 & 0.96 & 0.33 & -0.16 & 0.20 \\
J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.1 & 0.44 & 0.76 & 0.23 & -0.02 & 0.20 \\
J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.1 & 0.05 & 1.17 & 0.95 & 0.21 & -0.07 & 0.20 \\
J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.20 & -0.04 & 0.20 \\
J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.21 & 0.46 & 0.21 \\
J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1 & 8.70 & -0.02 & 0.20 \\
J032423.46+425429.6 & 51.1 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.22 & 0.80 & 0.20 \\ \hline
\end{tabular}
\end{table*}

\begin{table}[]
\centering
\caption{Tabulated data for the 3 stars observed using MAGELLAN/MIKE}
\label{data:magellan}
\begin{tabular}{lllllllllll}
designation\_1      & ra\_1\_1 & dec\_1\_1 & cannon\_teff\_1 & cannon\_logg\_1 & cannon\_m\_h\_1 & cannon\_alpha\_m\_1 & {[}Mg/Fe{]} & {[}K/Fe{]} & K\_FE & K\_FE\_err \\
J075043.12+204658.0 & 117.68   & 20.78     & 4795.00         & 2.53            & -0.47           & 0.06                & 0.15        & 0.80       & 1.11  & 0.05       \\
J120032.60+024438.2 & 180.14   & 2.74      & 4633.00         & 2.33            & -0.93           & 0.26                & 0.22        & 0.80       & 1.13  & 0.02       \\
J091825.49+172114.5 & 139.61   & 17.35     & 4899.00         & 2.71            & -1.19           & 0.29                & 0.36        & 1.54       & 1.30  & 0.12      
\end{tabular}
\end{table}

@@

>>>>

\subsection{Follow-up observations with Magellan/MIKE}
We acquired high-resolution spectra of three of our candidates as ancillary targets to an existing observing campaign. The three targets (J075043.12+204658.0, J120032.60+024438.2 and J091825.49+172114.5) were selected based on their observability from Las Campanas Observatory, and we used the Magellan Inamori Kyocera Echelle (MIKE) spectrograph on the Magellan Clay telescope \citep{shectman2003magellan,bernstein2003mike}. Exposure times were calculated to achieve a S/N of 30 per pixel at 450\,nm, sufficient to verify the K-enriched and Mg-poor nature of these stars. We reduced the data using the \texttt{CarPy} package \citep{kelson2003}. We used smoothing spline functions to continuum-normalize individual echelle orders, before combining them to produce a continuum-normalized spectrum that is contiguous from 350\,nm to 950\,nm. With the stellar parameters from \lamost, we calculated [K/Fe] and [Mg/Fe] abundances from individual atomic lines by measuring equivalent widths with Gaussian absorption profiles \citep{castelli2004,sneden,casey2014}. From the Magellan/MIKE spectra we confirmed that the K lines in these candidates were unaffected by telluric contamination. The estimated abundances from Magellan/MIKE spectra are consistent (within the uncertainties) of our initial abundance determinations from \lamost\ (Figure \ref{KvsMg}), and are presented in Table \ref{data:magellan}. Additional atomic line abundances are included in Table \ref{data:atomiclines} in the Appendix.
\begin{table}[H]
\centering
\caption{Summary of line abundances measured from Magellan/MIKE follow-up spectra.}
\label{data:magellan}
\begin{tabular}{lcccc}
\multicolumn{5}{c}{J075043.12+204658.0} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Mg}{I} & 5 & 7.45 & $+$0.32 & 0.10 \\
\ion{K}{I}  & 2 & 5.33 & $+$0.77 & 0.07 \\
\hline
\\
\multicolumn{5}{c}{J091825.48+172114.5} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Mg}{I} & 5 & 6.34 & $+$0.29 & 0.08 \\
\ion{K}{I}  & 2 & 6.28 & $+$0.85 & 0.11 \\
\hline
\\
\multicolumn{5}{c}{J120032.60+024438.2} \\
\hline
Species & $N$ & $\log_\epsilon(\textrm{X})$ & [X/Fe] & $\sigma/\sqrt{N}$ \\
\hline
\ion{Mg}{I} & 6 & 6.96 & $-$0.03 & 0.10 \\
\ion{K}{I}  & 2 & 4.96 & $+$1.22 & 0.31 \\
\hline
\end{tabular}
\end{table}

@@

\subsection{Detailed chemical abundances}
In this section, we describe the abundance trends evident from the \lamost\ and Magellan/MIKE spectra and compare with stars identified as anomalous regarding their [Mg/Fe] and [K/Fe] abundances in other studies. Abundances as well as several physical and observational parameters are available for all candidate stars online, with a sample shown in Table \ref{data:lamost}

\label{sec:abundances}

@@

\begin{figure}
\centering
\begin{subfigure}{0.35\textwidth}
\centering
	\includegraphics[width=\columnwidth]{NavsFeh.png}
    \caption{[Na/Fe] vs [Fe/H] for the candidate stars.}
    \label{NavsFeh}
\end{subfigure}

\begin{subfigure}{0.35\textwidth}
\centering
	\includegraphics[width=\columnwidth]{Navsb.png}
    \caption{[Na/Fe] vs galactic latitude for the candidate stars.}
    \label{Navsb}
\end{subfigure}

\begin{subfigure}{0.35\textwidth}
\centering
	\includegraphics[width=\columnwidth]{Navsradvel.png}
    \caption{[Na/Fe] vs radial velocity for the candidate stars.}
    \label{Navsradvel}
\end{subfigure}
%\end{figure*}
%\begin{figure*}
%\ContinuedFloat

\caption{A strong bimodality in [Na/Fe] abundances of the candidate stars is observed, with a significant population displaying anomolously high abundances. Due to the apparent near-exclusivity of this population within the disk of the galaxy, and their notably higher E(B-V) values \citep{schlafly2011}, this phenomena is almost certainly due to interstellar dust.}
\end{figure}

@@

The [K/Fe] abundance ratios in our sample also show an anti-correlation with total metallicity, illustrated in Figure \ref{KvsFe}, which is not present in the bulk of Milky Way stars. It is interesting that the levels of [K/Fe] in the Mg-poor population of NGC 2419 appear consistent with this relation. For completeness, we caution that this trend may be an artefact of our analysis. [K/Fe] is calculated from the flux residuals ( $f_{\textrm{residual}} = f_{\textrm{data}} - f_{\textrm{model}}$), and the data-driven model may already account for some level of [K/Fe] in the star due to the model representing the typical star at a given $\teff$, $\logg$, metalicity and [$\alpha$/Fe]. This has potential to cause spurious effects; however, it should also be emphasized that these effects would be within the uncertainties associated with estimating abundances from \lamost\ spectra. We recommend additional high-resolution observations to verify this trend.

@@

@@

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Additional atomic line abundances from Magellan/MIKE}

\begin{table*}
\centering
\caption{Atomic line abundances measured from Magellan/MIKE follow-up spectra of three Mg/K candidates.}
\label{data:atomiclines}
\begin{tabular}{crrrcccccc}
\hline
& & & & \multicolumn{2}{c}{J075043.12+204658.0} & \multicolumn{2}{c}{J091825.48+172114.5} & \multicolumn{2}{c}{J120032.60+024438.2} \\

Species & $\lambda$ & $\chi$ & $\log{gf}$ & E.W. & $\log_\epsilon(\textrm{X})$ & E.W. & $\log_\epsilon(\textrm{X})$ & E.W. & $\log_\epsilon(\textrm{X})$ \\
& $({\textrm \AA})$ & $(\textrm{eV})$ & & $(\textrm{m\AA})$ & & $(\textrm{m\AA})$ & & $(\textrm{m\AA})$ \\
\hline
\ion{Mg}{I} & 4057.51 & 4.346 & $-$0.890 & 208.5 & 7.71 & 154.4 & 6.66 & 167.6 & 6.95 \\
\ion{Mg}{I} & 4167.27 & 4.346 & $-$0.710 & 231.1 & 7.11 & 123.9 & 6.27 & 192.9 & 6.69 \\
\ion{Mg}{I} & 4571.10 &   0.0 & $-$5.623 & 208.4 & 7.71 & 154.4 & 6.66 & 167.6 & 6.95 \\
\ion{Mg}{I} & 4571.10 &   0.0 & $-$5.688 & 129.7 & 7.39 & 142.1 & 7.03 &  76.4 & 7.18 \\
\ion{Mg}{I} & 4702.99 & 4.330 & $-$0.380 & 231.1 & 7.11 & 123.9 & 6.27 & 192.9 & 6.69 \\
\ion{Mg}{I} & 4730.04 & 4.340 & $-$2.389 & 129.7 & 7.39 & 142.1 & 7.03 &  76.4 & 7.18 \\
\ion{Mg}{I} & 5528.41 & 4.340 & $-$0.498 &  80.0 & 7.68 & 175.9 & 6.65 & 115.0 & 7.09 \\
\ion{Mg}{I} & 5711.09 & 4.345 & $-$1.729 & 129.7 & 7.39 & 142.1 & 7.03 &  76.4 & 7.18 \\
\ion{Mg}{I} & 5711.09 & 4.340 & $-$1.724 & 129.3 & 7.38 & 165.1 &  6.4 & 204.5 & 6.91 \\
\ion{Mg}{I} & 6318.72 & 5.108 & $-$1.945 &  80.0 & 7.68 & 175.9 & 6.65 & 115.0 & 7.09 \\
\ion{K}{I}  & 7664.90 &   0.0 & $+$0.135 & 257.8 & 5.41 &  85.6 & 6.79 & 200.7 & 4.80 \\
\ion{K}{I}  & 7698.96 &   0.0 & $-$0.168 & 202.6 & 5.25 & 379.8 & 5.76 & 201.7 & 5.11 \\
\hline
\end{tabular}
\end{table*}

\begin{table*}
\centering
\caption{Tabulated data for 10 of the 112 candidate stars. Data for the full sample is available online.}
\label{data:lamost}
\begin{tabular}{cccccccccccccc}
\hline
\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{V$_\textrm{r}$} & \textbf{T$_\textrm{eff}$} & $\boldsymbol \log{ \, \textbf{g}}$ & \textbf{{[}Fe/H{]}} & \textbf{{[}$\alpha$/Fe{]}} & \textbf{$\boldsymbol \chi_r ^\textbf{2}$} & \textbf{{[}K/Fe{]}} & \textbf{Error} & \textbf{{[}Na/Fe{]}} & \textbf{Error} \\ 
- & {[}deg{]} & {[}deg{]} & [pixel$^{-1}]$ & {[${\rm km\,s}^{-1}$]} & {[}K{]} & $[{\rm cm\,s}^{-2}]$ & {[}dex{]} & {[}dex{]} & - & {[}dex{]} & {[}dex{]} & {[}dex{]} & {[}dex{]} \\ \hline
J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.26 & 0.86 & 0.23 \\
J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.22 & 0.39 & 0.22 \\
J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.21 & -0.20 & 0.20 \\
J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 & 0.96 & 0.33 & -0.16 & 0.20 \\
J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.1 & 0.44 & 0.76 & 0.23 & -0.02 & 0.20 \\
J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.1 & 0.05 & 1.17 & 0.95 & 0.21 & -0.07 & 0.20 \\
J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.20 & -0.04 & 0.20 \\
J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.21 & 0.46 & 0.21 \\
J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1 & 8.70 & -0.02 & 0.20 \\
J032423.46+425429.6 & 51.1 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.22 & 0.80 & 0.20 \\ \hline
\end{tabular}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
